Carrying out Latent Profile Analysis in Accordance With Best Practices: A Tutorial Using the tidyLPA R package

### 2020-01-28 paper.rmd
update

``` {r}
curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(3)
```

@@

``` {r, eval = FALSE}
curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(3, package = "MplusAutomation")
```

@@

```{r}
curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(3) %>% 
  plot_profiles()
```

@@

``` {r, compare-mclust, eval = FALSE}
curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(models = c(1, 2, 3, 6),
                    n_profiles = 1:9) %>%
  compare_solutions(statistics = c("AIC", "BIC"))
```

@@

``` {r, compare-mplus, eval = FALSE}
curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(models = c(1, 2, 3, 6),
                    n_profiles = 1:9, package = "mplus") %>%
  compare_solutions(statistics = c("AIC", "BIC"))
```

@@

``` {r}
m <- pisaUSA15[1:100, ] %>%
  select(broad_interest, enjoyment, self_efficacy) %>%
  single_imputation() %>%
  estimate_profiles(3:4)
```

>>>>

``` {r, curry-mac-mclust}
curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(3)
```

@@

``` {r, eval = FALSE, curry-mac-mplus}
curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(3, package = "MplusAutomation")
```

@@

```{r, curry_mac_p3}
curry_mac_three <- curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(3) %>% 
  plot_profiles()

curry_mac_three +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

@@

``` {r, compare-mclust, eval = FALSE}
curry_mac_solutions <- curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(models = c(1, 2, 3, 6),
                    n_profiles = 1:9) %>%
  compare_solutions(statistics = c("AIC", "BIC"))
```

The results of this analysis suggests that the Model 6, two or seven class models are best.

```{r, m6p7-solution}
curry_mac_m6p7 <- curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(3, 
                    variances = "varying",
                    covariances = "varying")

plot_profiles(curry_mac_m6p7)
```

```{r, m6p2-solution}
curry_mac_m6p2 <- curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(3, 
                    variances = "varying",
                    covariances = "varying")

plot_profiles(curry_mac_m6p7)
```

@@

``` {r, compare-mplus, eval = TRUE}
curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(models = c(1, 2, 3, 6),
                    n_profiles = 1:9, package = "mplus") %>%
  compare_solutions(statistics = c("AIC", "BIC"))
```

@@

``` {r, pisa-get-data}
m <- pisaUSA15[1:100, ] %>%
  select(broad_interest, enjoyment, self_efficacy) %>%
  single_imputation() %>%
  estimate_profiles(3:4)
```
